quollr: An R Package for Visualizing \(2-D\) Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-07 paper-quollr.Rmd
Deleted unnecessary data files
Added S-curve with different UMAP parameters

>>>>

Add the image generated with S-curve data

```{r}
#| label: scurve-diff-umap-layouts

scurve_umap1 <- read_rds("data/scurve/s_curve_noise_umap.rds")

nldr_scaled_obj <- gen_scaled_data(
  data = scurve_umap1)
umap_scaled1 <- nldr_scaled_obj$scaled_nldr

nldr1 <- umap_scaled1 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  theme(aspect.ratio = 1)

scurve_umap2 <- read_rds("data/scurve/s_curve_noise_umap2.rds")

nldr_scaled_obj2 <- gen_scaled_data(
  data = scurve_umap2)
umap_scaled2 <- nldr_scaled_obj2$scaled_nldr

nldr2 <- umap_scaled2 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  theme(aspect.ratio = 1)

scurve_umap3 <- read_rds("data/scurve/s_curve_noise_umap3.rds")

nldr_scaled_obj3 <- gen_scaled_data(
  data = scurve_umap3)
umap_scaled3 <- nldr_scaled_obj3$scaled_nldr

nldr3 <- umap_scaled3 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  theme(aspect.ratio = 1)

scurve_umap4 <- read_rds("data/scurve/s_curve_noise_umap4.rds")

nldr_scaled_obj4 <- gen_scaled_data(
  data = scurve_umap4)
umap_scaled4 <- nldr_scaled_obj4$scaled_nldr

nldr4 <- umap_scaled4 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  theme(aspect.ratio = 1)

scurve_umap5 <- read_rds("data/scurve/s_curve_noise_umap5.rds")

nldr_scaled_obj5 <- gen_scaled_data(
  data = scurve_umap5)
umap_scaled5 <- nldr_scaled_obj5$scaled_nldr

nldr5 <- umap_scaled5 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#636363') +
  theme(aspect.ratio = 1)

scurve_umap6 <- read_rds("data/scurve/s_curve_noise_umap6.rds")

nldr_scaled_obj6 <- gen_scaled_data(
  data = scurve_umap6)
umap_scaled6 <- nldr_scaled_obj6$scaled_nldr

nldr6 <- umap_scaled6 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  theme(aspect.ratio = 1)
```

```{r}
nldr1 + nldr2 + nldr3 + 
  nldr4 + nldr5 + nldr6 +
  plot_layout(ncol = 3)
```

### 2025-05-07 paper-quollr.tex
Added S-curve with different UMAP parameters

@@

\begin{verbatim}
#> $df_bin
#> # A tibble: 72 x 8
#>    hb_id     x1    x2    x3        x4        x5        x6         x7
#>    <int>  <dbl> <dbl> <dbl>     <dbl>     <dbl>     <dbl>      <dbl>
#>  1    13  0.996  1.77  1.07 -0.0117    0.00979  -0.0725   -0.00321  
#>  2    14  0.829  1.79  1.50 -0.000753 -0.00194  -0.00936  -0.000454 
#>  3    15  0.307  1.78  1.94 -0.00384   0.00212  -0.00117  -0.000159 
#>  4    16 -0.175  1.74  1.98  0.00143   0.00320   0.00450  -0.0000763
#>  5    18 -0.493  1.78  1.87 -0.0100    0.000680  0.0799   -0.000835 
#>  6    26  0.962  1.22  1.22  0.00107  -0.00260  -0.000948  0.000234 
#>  7    27  0.631  1.28  1.75  0.000266  0.00174  -0.00158   0.00114  
#>  8    28  0.139  1.20  1.97 -0.00183   0.000279  0.00177  -0.000666 
#>  9    29 -0.187  1.00  1.98 -0.00228   0.00461  -0.0506   -0.00472  
#> 10    30 -0.562  1.23  1.82 -0.000563  0.00166  -0.00923  -0.000111 
#> # i 62 more rows
#> 
#> $df_bin_centroids
#> # A tibble: 72 x 6
#>    hexID      c_x      c_y bin_counts std_counts drop_empty
#>    <int>    <dbl>    <dbl>      <int>      <dbl> <lgl>     
#>  1    13 -0.0455  0.000514          2     0.0194 FALSE     
#>  2    14  0.0634  0.000514         81     0.786  FALSE     
#>  3    15  0.172   0.000514         56     0.544  FALSE     
#>  4    16  0.281   0.000514         55     0.534  FALSE     
#>  5    18  0.499   0.000514          2     0.0194 FALSE     
#>  6    26  0.00894 0.0949           70     0.680  FALSE     
#>  7    27  0.118   0.0949           78     0.757  FALSE     
#>  8    28  0.227   0.0949           86     0.835  FALSE     
#>  9    29  0.336   0.0949            5     0.0485 FALSE     
#> 10    30  0.445   0.0949           54     0.524  FALSE     
#> # i 62 more rows
\end{verbatim}

@@

\begin{verbatim}
#> $bin2
#> [1] 13
#> 
#> $a1
#> [1] 0.1089367
#> 
#> $a2
#> [1] 0.09434198
\end{verbatim}

@@

\begin{verbatim}
#> $a1
#> [1] 0.1089367
#> 
#> $a2
#> [1] 0.09434198
#> 
#> $bins
#> [1] 12 13
#> 
#> $start_point
#> [1] -0.10000000 -0.09382762
#> 
#> $centroids
#> # A tibble: 156 x 3
#>    hexID      c_x     c_y
#>    <int>    <dbl>   <dbl>
#>  1     1 -0.1     -0.0938
#>  2     2  0.00894 -0.0938
#>  3     3  0.118   -0.0938
#>  4     4  0.227   -0.0938
#>  5     5  0.336   -0.0938
#>  6     6  0.445   -0.0938
#>  7     7  0.554   -0.0938
#>  8     8  0.663   -0.0938
#>  9     9  0.771   -0.0938
#> 10    10  0.880   -0.0938
#> # i 146 more rows
#> 
#> $hex_poly
#> # A tibble: 936 x 3
#>    hex_poly_id        x       y
#>          <int>    <dbl>   <dbl>
#>  1           1 -0.1     -0.0309
#>  2           1 -0.154   -0.0624
#>  3           1 -0.154   -0.125 
#>  4           1 -0.1     -0.157 
#>  5           1 -0.0455  -0.125 
#>  6           1 -0.0455  -0.0624
#>  7           2  0.00894 -0.0309
#>  8           2 -0.0455  -0.0624
#>  9           2 -0.0455  -0.125 
#> 10           2  0.00894 -0.157 
#> # i 926 more rows
#> 
#> $data_hb_id
#> # A tibble: 3,750 x 4
#>      emb1   emb2    ID hb_id
#>     <dbl>  <dbl> <int> <int>
#>  1 0.276  0.915      1   136
#>  2 0.927  0.347      2    70
#>  3 0.810  0.242      3    45
#>  4 0.137  0.657      5    99
#>  5 0.476  0.799      6   114
#>  6 0.0485 0.0657     7    26
#>  7 0.737  0.851      9   129
#>  8 0.833  0.224     10    45
#>  9 0.909  0.371     11    70
#> 10 0.0890 0.194     12    38
#> # i 3,740 more rows
#> 
#> $std_cts
#> # A tibble: 72 x 3
#>    hb_id     n std_counts
#>    <int> <int>      <dbl>
#>  1    13     2     0.0194
#>  2    14    81     0.786 
#>  3    15    56     0.544 
#>  4    16    55     0.534 
#>  5    18     2     0.0194
#>  6    26    70     0.680 
#>  7    27    78     0.757 
#>  8    28    86     0.835 
#>  9    29     5     0.0485
#> 10    30    54     0.524 
#> # i 62 more rows
#> 
#> $tot_bins
#> [1] 156
#> 
#> $non_bins
#> [1] 72
#> 
#> $pts_bins
#> # A tibble: 72 x 2
#>    hb_id pts_list  
#>    <int> <list>    
#>  1    13 <int [2]> 
#>  2    14 <int [81]>
#>  3    15 <int [56]>
#>  4    16 <int [55]>
#>  5    18 <int [2]> 
#>  6    26 <int [70]>
#>  7    27 <int [78]>
#>  8    28 <int [86]>
#>  9    29 <int [5]> 
#> 10    30 <int [54]>
#> # i 62 more rows
#> 
#> attr(,"class")
#> [1] "hex_bin_obj"
\end{verbatim}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-20-1}

>>>>

Add the image generated with S-curve data

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-1-1}

@@

\begin{verbatim}
#> $df_bin
#> # A tibble: 86 x 8
#>    hb_id       x1    x2    x3        x4        x5        x6        x7
#>    <int>    <dbl> <dbl> <dbl>     <dbl>     <dbl>     <dbl>     <dbl>
#>  1    15  0.968   0.198  1.21  0.000518  0.00161   0.00240  -0.000547
#>  2    16  0.730   0.142  1.67 -0.000689  0.000495  0.00168   0.000794
#>  3    17  0.323   0.158  1.94 -0.00265  -0.00523  -0.00942  -0.00115 
#>  4    18 -0.203   0.154  1.98 -0.00269  -0.00107  -0.0382   -0.00167 
#>  5    19 -0.628   0.114  1.78 -0.000131 -0.00323   0.0347   -0.00288 
#>  6    27  0.987   0.579  1.14 -0.00124  -0.00121   0.0199   -0.00363 
#>  7    28  0.847   0.537  1.51  0.000374 -0.00215  -0.00901  -0.000548
#>  8    29  0.469   0.476  1.87  0.00117  -0.000439 -0.0191    0.000251
#>  9    30 -0.00747 0.491  1.99 -0.000570  0.00114  -0.000815  0.000786
#> 10    31 -0.525   0.449  1.84  0.00141  -0.000575 -0.0112    0.000714
#> # i 76 more rows
#> 
#> $df_bin_centroids
#> # A tibble: 86 x 6
#>    hexID   c_x      c_y bin_counts std_counts drop_empty
#>    <int> <dbl>    <dbl>      <int>      <dbl> <lgl>     
#>  1    15 0.158 0.000959         43     0.518  FALSE     
#>  2    16 0.262 0.000959         35     0.422  FALSE     
#>  3    17 0.365 0.000959         21     0.253  FALSE     
#>  4    18 0.468 0.000959         11     0.133  FALSE     
#>  5    19 0.571 0.000959          8     0.0964 FALSE     
#>  6    27 0.107 0.0904           10     0.120  FALSE     
#>  7    28 0.210 0.0904           56     0.675  FALSE     
#>  8    29 0.313 0.0904           43     0.518  FALSE     
#>  9    30 0.416 0.0904           54     0.651  FALSE     
#> 10    31 0.520 0.0904           42     0.506  FALSE     
#> # i 76 more rows
\end{verbatim}

@@

\begin{verbatim}
#> $bin2
#> [1] 13
#> 
#> $a1
#> [1] 0.1032943
#> 
#> $a2
#> [1] 0.08945548
\end{verbatim}

@@

\begin{verbatim}
#> $a1
#> [1] 0.1032943
#> 
#> $a2
#> [1] 0.08945548
#> 
#> $bins
#> [1] 12 13
#> 
#> $start_point
#> [1] -0.10000000 -0.08849688
#> 
#> $centroids
#> # A tibble: 156 x 3
#>    hexID      c_x     c_y
#>    <int>    <dbl>   <dbl>
#>  1     1 -0.1     -0.0885
#>  2     2  0.00329 -0.0885
#>  3     3  0.107   -0.0885
#>  4     4  0.210   -0.0885
#>  5     5  0.313   -0.0885
#>  6     6  0.416   -0.0885
#>  7     7  0.520   -0.0885
#>  8     8  0.623   -0.0885
#>  9     9  0.726   -0.0885
#> 10    10  0.830   -0.0885
#> # i 146 more rows
#> 
#> $hex_poly
#> # A tibble: 936 x 3
#>    hex_poly_id        x       y
#>          <int>    <dbl>   <dbl>
#>  1           1 -0.1     -0.0289
#>  2           1 -0.152   -0.0587
#>  3           1 -0.152   -0.118 
#>  4           1 -0.1     -0.148 
#>  5           1 -0.0484  -0.118 
#>  6           1 -0.0484  -0.0587
#>  7           2  0.00329 -0.0289
#>  8           2 -0.0484  -0.0587
#>  9           2 -0.0484  -0.118 
#> 10           2  0.00329 -0.148 
#> # i 926 more rows
#> 
#> $data_hb_id
#> # A tibble: 3,750 x 4
#>     emb1   emb2    ID hb_id
#>    <dbl>  <dbl> <int> <int>
#>  1 0.270 0.839      1   125
#>  2 0.788 0.466      2    82
#>  3 0.771 0.319      3    69
#>  4 0.306 0.542      5    88
#>  5 0.549 0.806      6   127
#>  6 0.166 0.259      7    52
#>  7 0.672 0.596      9   104
#>  8 0.735 0.354     10    69
#>  9 0.839 0.467     11    82
#> 10 0.240 0.0903    12    28
#> # i 3,740 more rows
#> 
#> $std_cts
#> # A tibble: 86 x 3
#>    hb_id     n std_counts
#>    <int> <int>      <dbl>
#>  1    15    43     0.518 
#>  2    16    35     0.422 
#>  3    17    21     0.253 
#>  4    18    11     0.133 
#>  5    19     8     0.0964
#>  6    27    10     0.120 
#>  7    28    56     0.675 
#>  8    29    43     0.518 
#>  9    30    54     0.651 
#> 10    31    42     0.506 
#> # i 76 more rows
#> 
#> $tot_bins
#> [1] 156
#> 
#> $non_bins
#> [1] 86
#> 
#> $pts_bins
#> # A tibble: 86 x 2
#>    hb_id pts_list  
#>    <int> <list>    
#>  1    15 <int [43]>
#>  2    16 <int [35]>
#>  3    17 <int [21]>
#>  4    18 <int [11]>
#>  5    19 <int [8]> 
#>  6    27 <int [10]>
#>  7    28 <int [56]>
#>  8    29 <int [43]>
#>  9    30 <int [54]>
#> 10    31 <int [42]>
#> # i 76 more rows
#> 
#> attr(,"class")
#> [1] "hex_bin_obj"
\end{verbatim}

@@
